---
title: "C1 -  read in 'Yellow sheets'"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output:
  pdf_document: default
---

*Run this script chuck by chunk, so it is possible to check*

# Intro
This program reads in data from the submitted templates 'Yellow sheet' and standardize the codes. Countries have a tendency to submit sheets in different orders, with different names and also using slightly difffernt templates (e.g. number of rows)- therefore the import differes between country and data type, which gives a lot of import lines\

Five functions read in the data from the template

1. read_in_canum(path, sheets, noAgeClasses)\
2. read_in_catch(path, sheets, noAreas)\
3. read_in_areaOfficial(path, sheets, noRectangles)
4. read_in_samples<-function(path, sheets, firstLineSamples)
5. read_in_length<-function(path, sheets, firstLineLength)


path - path+filename\
sheets - a vector with the number of the sheets where the data can be found. The order and number of submitted sheets varies between country\
noAgeClasses - for SD20-24 there are normally 9 classes (wr 0-8+), but some countries have more lines.\
noAreas - number of areas in the catch sheet\
noRectangles - Number of rectangles on the sheet="areaOfficial"
firstLineLength - 1st line with length in the excel sheet


2018/03/08 - Added a function, which reads in samples from the updated 'Yellow sheet' template - before samples were in a seperate file.

2018/03/08 - Added a part for merging Swedish C and D fleet in 2017

2018/03/08 - Changed the handling of NA, so e.g. WECA and LECA are not filled in with 0

2018/03/08 - Added SOP correction on canum_1000 - not canum.

2018/03/12 - Added a function, which reads in the length distrubution from the length sheets

2018/03/15 - Added a function, which reads in the catch per rectangle from the sheet="areaOfficial"

2018/03/15 - File names are now only in the beginning

```{r setup, include=F}

library(sqldf)
library(dplyr)
library(knitr)

options("scipen" = 1000, digits = 4)

year <- 2018

rawDataPath <- "Q:/mynd/Assessement_discard_and_the_like/WG/HAWG/WBSS_SC/wg_HAWG/WBSS/compile_input_data/catch/data/2019/yellow_sheets/"
dataPath <- "Q:/mynd/Assessement_discard_and_the_like/WG/HAWG/WBSS_SC/wg_HAWG/WBSS/compile_input_data/catch/data/2019/results/"

source("Q:/mynd/Assessement_discard_and_the_like/WG/HAWG/WBSS_SC/wg_HAWG/WBSS/compile_input_data/catch/scripts/WBSS_functions_data.R")

knitr::opts_chunk$set(echo = F, warning = F, message = F, results = 'asis')

```


```{r}

# File names
dnkFile <- "DC_Annex 7.1.3. HAWG Template_her_2024_DNK_2018.xls"
gerFile <- "2_2019 DC HAWG her.27.2024 DE AC4_small revision.xls"
polFile <- "DC_Annex 7.1.3. HAWG Template_her_2024_poland.xls"
sweFile <- "DC_Annex_7.1.3_HAWG_SWE_her.27.20-24_2018.xls"
norFile <- "DC_Annex 5_Template_her.27.2024_Norway_2018.xls"
froFile <- "DC_Annex 7.1.3. HAWG Template_her_2024_FO_2018.xls"
```


# Read in data
## Canum 
read in data from canum sheet(s) in template - only countries with catches - in 2018 DNK, FRO, GER, NOR, POL and SWE

```{r read in canum, include=F}

dnk <-
  read_in_canum(
    paste(rawDataPath, dnkFile, sep = ""),
    sheets = c(6, 7, 8, 9, 10, 11, 12),
    noAgeClasses = 9
  )

ger <-
  read_in_canum(
    paste(rawDataPath, gerFile, sep = ""),
    sheets = c(7:13),
    noAgeClasses = 9
  )

pol <-
  read_in_canum(
    paste(rawDataPath, polFile, sep = ""),
    sheets = c(6:12),
    noAgeClasses = 9
  )

swe <-
  read_in_canum(
    paste(rawDataPath, sweFile, sep = ""),
    sheets = c(6:12),
    noAgeClasses = 9
  )

nor <-
  read_in_canum(
    paste(rawDataPath, norFile, sep = ""),
    sheets = c(6:12),
    noAgeClasses = 9
  )

fro <-
  read_in_canum(
    paste(rawDataPath, froFile, sep = ""),
    sheets = c(7),
    noAgeClasses = 9
    )

```

## Read in samples
Number of samples are in the CANUM sheets from 2018
```{r, read in samples, include=F}


dnkS <-
  read_in_samples(
    paste(rawDataPath, dnkFile, sep = ""),
    sheets = c(6, 7, 8, 9, 10, 11, 12),
    firstLineSamples = 27
  )

gerS <-
  read_in_samples(
    paste(rawDataPath, gerFile, sep = ""),
    sheets = c(7:13),
    firstLineSamples = 27
  )

polS <-
  read_in_samples(
    paste(rawDataPath, polFile, sep = ""),
    sheets = c(6:12),
    firstLineSamples = 27
  )

sweS <-
  read_in_samples(
    paste(rawDataPath, sweFile, sep = ""),
    sheets = c(6:12),
    firstLineSamples = 27
  )

norS <-
  read_in_samples(
    paste(rawDataPath, norFile, sep = ""),
    sheets = c(6:12),
    firstLineSamples = 27
  )

froS <-
  read_in_samples(
    paste(rawDataPath, froFile, sep = ""),
    sheets = c(7),
    firstLineSamples = 27
  )
```

## Read in catch
Read in data from catch sheet in template
```{r read in catch, include=F}
dnkC <-
  read_in_catch(paste(rawDataPath, dnkFile, sep = ""),
                sheets = 3,
                noAreas = 29)

gerC <-
  read_in_catch(paste(rawDataPath, gerFile, sep = ""),
                sheets = 3,
                noAreas = 29)

polC <-
  read_in_catch(paste(rawDataPath, polFile, sep = ""),
                sheets = c(3),
                noAreas = 29)

sweC <-
  read_in_catch(paste(rawDataPath, sweFile, sep = ""),
                sheets = c(3),
                noAreas = 29)

norC <-
  read_in_catch(paste(rawDataPath, norFile, sep = ""),
                sheets = c(3),
                noAreas = 29)

froC <-
  read_in_catch(paste(rawDataPath, froFile, sep = ""),
                sheets = c(3),
                noAreas = 29)
```

## Read in length
Read in the length distribution from the length sheets

20190310: Not read. DNK and GER missing.

```{r read in length}

# dnkL <-
#   read_in_length(
#     paste(rawDataPath, dnkFile, sep = ""),
#     sheets = c(6, 8, 10, 12, 14, 16, 18),
#     firstLineLength = 10
#   )
# 
# gerL <-
#   read_in_length(
#     paste(rawDataPath, gerFile, sep = ""),
#     sheets = c(5:6),
#     firstLineLength = 10
#   )
# 
# polL <-
#   read_in_length(
#     paste(rawDataPath, polFile, sep = ""),
#     sheets = c(5),
#     firstLineLength = 10
#   )
# 
# sweL <-
#   read_in_length(
#     paste(rawDataPath, sweFile, sep = ""),
#     sheets = c(5:9),
#     firstLineLength = 10
#   )
# 
# norL <-
#   read_in_length(
#     paste(rawDataPath, norFile, sep = ""),
#     sheets = c(5),
#     firstLineLength = 10
#   )
```


## Read in landings per square from area_official

20190310: Info from Germany and Faroy island missing

```{r read in catch per square, include=F}

dnkR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, dnkFile, sep = ""),
    sheets = c(13),
    noRectangles = 1182
  )

gerR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, gerFile, sep = ""),
    sheets = c(14),
    noRectangles = 1182
  )

polR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, polFile, sep = ""),
    sheets = c(13),
    noRectangles = 1182
  )

sweR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, sweFile, sep = ""),
    sheets = c(13),
    noRectangles = 1182
  )

norR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, norFile, sep = ""),
    sheets = c(13),
    noRectangles = 1183
  )

froR <-
  read_in_areaOfficial(
    path = paste(rawDataPath, froFile, sep = ""),
    sheets = c(13),
    noRectangles = 1182
  )
```

# Combine and recode canum
```{r, include=F}
canum <- rbind(dnk, ger, pol, swe, nor, fro)

unique(canum$ctry)

unique(canum$sppName)

distinct(canum, ctry, sppName)

canum$sppName <- ifelse(canum$sppName %in% c("Herring (Clupea harengus)", "Herring south of 62N", "Clupea harengus"), "Herring", canum$sppName)

unique(canum$sppName)

unique(canum$year)

unique(canum$area)

canum$area <-
  ifelse(
    canum$area %in% c("SD 20", "IIIaN", "IIIa"),
    "27.3.a.20",
    ifelse(
      canum$area %in% c("SD 21", "IIIaS"),
      "27.3.a.21",
      ifelse(
        canum$area %in% c("SD 22", "BAL22"),
        "27.3.c.22",
        ifelse(
          canum$area %in% c("SD 23", "BAL23"),
          "27.3.b.23",
          ifelse(canum$area %in% c("SD 24", "BAL24"), "27.3.d.24", canum$area)
        )
      )
    )
  )

unique(canum$area)

distinct(canum, area, fleet)

canum$fleet <-
  ifelse(
    canum$area %in% c("27.3.a.20", "27.3.a.21") &
      canum$fleet %in% c("C", "Fleet-C", "> 32 mm", "Fleet-A"),
    "C",
    ifelse(
      canum$area %in% c("27.3.a.20", "27.3.a.21") &
        canum$fleet %in% c("D", "Fleet-D", "< 32mm", "< 32 mm"),
      "D",
      ifelse(
        canum$area %in% c("27.3.c.22", "27.3.b.23", "27.3.d.24", "all"),
        "F",
        canum$fleet
      )
    )
  )

distinct(canum, area, fleet)

unique(canum$wr)

canum$wr <- ifelse(canum$wr %in% c("8.000000", "8"), "8+", canum$wr)

unique(canum$wr)

##Handling units

unique(canum$canum_unit)

unit <- distinct(canum, ctry, canum_unit)

#subset(canum, canum_unit=="(1000)")

canum$canum_1000 <- ifelse(canum$canum_unit == "(millions)", canum$canum*1000, canum$canum)

unique(canum$weca_unit)
weca_unit <- distinct(canum, ctry, weca_unit)
canum$weca_g <-
  ifelse(canum$weca_unit %in% c("(Kg)", "(kg)"),
         canum$weca * 1000,
         canum$weca)

unique(canum$leca_unit)
canum$leca_cm <- ifelse(canum$leca_unit != "(cm)", "", canum$leca)

unique(canum$catch_unit)
canum$catch_t <- ifelse(canum$catch_unit != "(t)", "", canum$catch)

##Add zero's to canum
canum <- subset(canum,!is.na(wr))

year <- distinct(canum, year)
ctry <- distinct(canum, ctry)
sppName <- distinct(canum, sppName)
fleet <- distinct(canum, fleet, area)
wr <- distinct(canum, wr)
quarter <- distinct(canum, quarter)

dummy <-
  sqldf("select * from year, ctry, sppName, fleet, wr, quarter")

canum0 <-
  canum[, c("year", "ctry", "sppName", "fleet", "area", "wr", "quarter")]
dummy1 <- setdiff(dummy, canum0)

canum1 <- bind_rows(canum, dummy1)

#Replace NA for certain variables

canum1$canum <- ifelse(is.na(canum1$canum), 0, canum1$canum)
canum1$canum_1000 <-
  ifelse(is.na(canum1$canum_1000), 0, canum1$canum_1000)
canum1$catch_t <- ifelse(is.na(canum1$catch_t), 0, canum1$catch_t)

```


# Combine and recode sample
```{r, include=F}
samp <- rbind(dnkS, gerS, polS, sweS, norS, froS)

unique(samp$noSample)

samp$noSample <- ifelse(samp$noSample == -9, 0, samp$noSample)
samp$noLength <- ifelse(samp$noLength == -9, 0, samp$noLength)
samp$noAge <- ifelse(samp$noAge == -9, 0, samp$noAge)

unique(samp$noSample)

unique(samp$ctry)

unique(samp$sppName)

samp$sppName <-
  ifelse(
    samp$sppName %in% c(
      "Herring (Clupea harengus)",
      "Herring south of 62N",
      "Clupea harengus"
    ),
    "Herring",
    samp$sppName
  )

unique(samp$sppName)

unique(samp$year)

unique(samp$area)

samp$area <-
  ifelse(
    samp$area %in% c("SD 20", "IIIaN", "IIIa"),
    "27.3.a.20",
    ifelse(
      samp$area %in% c("SD 21", "IIIaS"),
      "27.3.a.21",
      ifelse(
        samp$area %in% c("SD 22", "BAL22"),
        "27.3.c.22",
        ifelse(
          samp$area %in% c("SD 23", "BAL23"),
          "27.3.b.23",
          ifelse(samp$area %in% c("SD 24", "BAL24"), "27.3.d.24", samp$area)
        )
      )
    )
  )

unique(samp$area)

distinct(samp, area, fleet)

#subset(samp, fleet=="All")

samp$fleet <-
  ifelse(
    samp$area %in% c("27.3.a.20", "27.3.a.21") &
      samp$fleet %in% c("C", "Fleet-C", "> 32 mm", "Fleet-A"),
    "C",
    ifelse(
      samp$area %in% c("27.3.a.20", "27.3.a.21") &
        samp$fleet %in% c("D", "Fleet-D", "< 32mm", "< 32 mm"),
      "D",
      ifelse(
        samp$area %in% c("27.3.c.22", "27.3.b.23", "27.3.d.24"),
        "F",
        samp$fleet
      )
    )
  )

distinct(samp, area, fleet)
```

# Combine and recode length

20190310: Not done

```{r, include=F}
# 
# length<-rbind(dnkL,gerL,polL,sweL,norL)
# 
# unique(length$ctry)
# 
# unique(length$sppName)
# 
# length$sppName<-ifelse(length$sppName=="Herring (Clupea harengus)", "Herring", length$sppName)
# 
# unique(length$sppName)
# 
# unique(length$year)
# 
# unique(length$area)
# 
# length$area<-ifelse(length$area %in% c("SD20","SD 20","IIIaN"), "27.3.a.20",
#                    ifelse(length$area %in% c("SD21","SD 21","IIIaS"), "27.3.a.21", 
#                    ifelse(length$area %in% c("SD22","SD 22","BAL22"), "27.3.c.22",
#                    ifelse(length$area %in% c("SD23","SD 23","BAL23"), "27.3.b.23",
#                    ifelse(length$area %in% c("SD24","SD 24","BAL24"), "27.3.d.24", length$area)))))
# unique(length$area)
# 
# distinct(length, area, fleet)
# 
# length$fleet<-ifelse(length$area %in% c("27.3.a.20","27.3.a.21") & length$fleet %in% c("C","Fleet-C","> 32 mm", "C-fleet", "Fleet C"), "C",
#                     ifelse(length$area %in% c("27.3.a.20","27.3.a.21") & length$fleet %in% c("D","Fleet-D","< 32mm","< 32 mm", "D-fleet"), "D",
#                     ifelse(length$area %in% c("27.3.c.22","27.3.b.23","27.3.d.24"),"F", length$fleet)))
# 
# distinct(length, area, fleet)
# 
# ##Handling units
# 
# length$clnum[is.na(length$clnum)]<-0
# 
# unique(length$clnum_unit)
# 
# length$clnum_1000<-ifelse(length$length_unit=="(millions)", length$clnum*1000, length$clnum)

```

# Combine and recode catch

```{r, include=F}
catch <- rbind(dnkC, polC, gerC, sweC, norC, froC)

str(catch)

catch$landWt <- as.numeric(catch$landWt)
catch$unallocCatchWt <- as.numeric(catch$unallocCatchWt)
catch$misRepCatchWt <- as.numeric(catch$misRepCatchWt)
catch$disWt <- as.numeric(catch$disWt)

str(catch)

##Check codes in catch

unique(catch$area)

catch$area <- ifelse(
  catch$area == "IIIa/Skagerak",
  "27.3.a.20",
  ifelse(catch$area == "IIIa/Kattegat", "27.3.a.21", catch$area)
)


catch$area <- ifelse(
  catch$area %in% c("SD 20", "IIIaN"),
  "27.3.a.20",
  ifelse(
    catch$area %in% c("SD 21", "IIIaS"),
    "27.3.a.21",
    ifelse(
      catch$area %in% c("22", "SD 22", "BAL22"),
      "27.3.c.22",
      ifelse(
        catch$area %in% c("23", "SD 23", "BAL23"),
        "27.3.b.23",
        ifelse(
          catch$area %in% c("24", "SD 24", "BAL24"),
          "27.3.d.24",
          catch$area
        )
      )
    )
  )
)
unique(catch$area)

catch[is.na(catch)] <- 0

catch$catch <-
  catch$landWt + catch$unallocCatchWt + catch$misRepCatchWt + catch$disWt

```

# Combine and recode rect

```{r, include=F}
rect <- rbind(dnkR, polR, gerR, sweR, norR, froR)

str(rect)

##Check codes in rect

unique(rect$unit)

rect$catch_t <-
  ifelse(rect$unit == "(millions)", rect$landWt * 1000, rect$landWt)

```


# Merge samples with canum

Before 2018: Number of samples are made in a seperate csv files, since the template do not support the aggregation needed

2018 & after: Number of samples are in general in then canum sheets

```{r, include=F}

canum2 <- merge(canum1, samp, all.x = T)

canum2$noSample <- ifelse(is.na(canum2$noSample), 0, canum2$noSample)
canum2$noLength <- ifelse(is.na(canum2$noLength), 0, canum2$noLength)
canum2$noAge <- ifelse(is.na(canum2$noAge), 0, canum2$noAge)
```


# Merge length and samples

Not done 
```{r, include=F}
# length1<-merge(length,samp, all.x=T)
# 
# length1$noSample<-ifelse(is.na(length1$noSample), 0, length1$noSample)
# length1$noLength<-ifelse(is.na(length1$noLength), 0, length1$noLength)
# length1$noAge<-ifelse(is.na(length1$noAge), 0, length1$noAge)
```

# Combine Swedish fleet C and D

*Same procedure as last year*

```{r combine swe, include=F}

sw <-
  subset(canum2, ctry == "Sweden" &
           area %in% c("27.3.a.20", "27.3.a.21"))
rest <-
  subset(canum2,!(ctry == "Sweden" &
                    area %in% c("27.3.a.20", "27.3.a.21")))

swC <-
  aggregate(cbind((catch), (catch_t)) ~ ctry + sppName + year + area + quarter +
              catch_unit, data = sw, function(x)
                sum(x) / 9)
swC <- rename(swC, catch = V1, catch_t = V2)

swCA <-
  aggregate(
    cbind(canum, canum_1000, noSample, noLength, noAge) ~ ctry + sppName + year +
      area + quarter + wr + canum_unit,
    data = sw,
    FUN = sum
  )

swBio <-
  distinct(
    subset(sw, weca != 0),
    ctry,
    sppName,
    year,
    area,
    quarter,
    wr,
    leca,
    weca,
    leca_unit,
    weca_unit,
    weca_g,
    leca_cm
  )

sw1 <- left_join(left_join(swC, swCA), swBio)

sw1 <- arrange(sw1, ctry, sppName, year, area, quarter, wr)
sw1$fleet <- "C"

#Empty lines with fleet D
swd <- sw1
swd$catch <- 0
swd$catch_t <- 0
swd$canum <- 0
swd$canum_1000 <- 0
swd$noSample <- 0
swd$noLength <- 0
swd$noAge <- 0
swd$weca <- NA
swd$leca <- NA
swd$weca_g <- NA
swd$leca_cm <- NA
swd$fleet <- "D"

canum2 <- rbind(rbind(rest, sw1), swd)
```

```{r, echo = F, results = "asis"}

kable(summarise(group_by(sw, ctry, year, fleet, area, quarter), ton = sum(catch)/9), caption = "Landings per fleet before merge")

```


# SOP correction
Note the Swedish SOP correction cab be big due to the fact that not all fleet D had biology from fleet C, which I assumed

```{r, include=F}

sop <-
  aggregate(((canum_1000 * weca_g) / 1000) ~ ctry + sppName + year + area +
              quarter + fleet + catch_t,
            data = canum2,
            FUN = sum
  )

colnames(sop) <-
  c("ctry",
    "sppName",
    "year",
    "area",
    "quarter",
    "fleet",
    "catch_t",
    "sop")
sop$sop <- as.numeric(sop$sop)

canum3 <- merge(canum2, sop, all.x = T)
canum3$sopCorr <- (canum3$catch_t / canum3$sop)
canum3$canum_1000 <-
  ifelse(
    canum3$canum_1000 > 0,
    canum3$canum_1000 * (canum3$catch_t / canum3$sop),
    canum3$canum_1000
  )

testSop <-
  aggregate(((canum_1000 * weca_g) / 1000) ~ ctry + sppName + year + area +
              quarter + fleet + catch_t,
            data = canum3,
            FUN = sum
  )
```


# Output data
```{r}
saveRDS(canum3,
        paste(
          dataPath,
          "C1_her2024_canum_without_imputations_", year, ".rds",
          sep = ""
        ))

write.table(
  canum3,
  paste(
    dataPath,
    "C1_her2024_canum_without_imputations_", year, ".csv",
    sep = ""
  ),
  sep = ",",
  row.names = F,
  na = ""
)

saveRDS(sw,
        paste(
          dataPath,
          "C1_SWE_her2024_fleet_C_D_before_merge_", year, ".rds",
          sep = ""
        ))

write.table(
  sw,
  paste(
    dataPath,
    "C1_SWE_her2024_fleet_C_D_before_merge_", year, ".csv",
    sep = ""
  ),
  sep = ",",
  row.names = F,
  na = ""
)

saveRDS(samp, paste(dataPath, "C1_her2024_samples_", year, ".rds", sep = ""))
write.table(
  samp,
  paste(dataPath, "C1_her2024_samples_", year, ".csv", sep = ""),
  sep = ",",
  row.names = F,
  na = ""
)

saveRDS(catch, paste(dataPath, "C1_her2024_catch_", year, ".rds", sep = ""))
write.table(
  catch,
  paste(dataPath, "C1_her2024_catch_", year, ".csv", sep = ""),
  sep = ",",
  row.names = F,
  na = ""
)

# saveRDS(length1,
#         paste(dataPath, "C1_her2024_length_", year, ".rds", sep = ""))
# write.table(
#   length1,
#   paste(dataPath, "C1_her2024_length_", year, ".csv", sep = ""),
#   sep = ",",
#   row.names = F,
#   na = ""
# )
```


