---
title: "C2 -  checks'"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output: pdf_document
---

```{r setup, include=F}
library(sqldf)
library(dplyr)
library(knitr)
library(ggplot2)

options("scipen"=1000, digits=4)

dataPath <- "Q:/mynd/Assessement_discard_and_the_like/WG/HAWG/WBSS_SC/wg_HAWG/WBSS/compile_input_data/catch/data/2019/results/"

```

```{r import data, include=F}
canum <-
  readRDS(paste(
    dataPath,
    "C1_her2024_canum_without_imputations_2018.rds",
    sep = ""
  ))
catch <- filter(readRDS(paste(dataPath, "C1_her2024_catch_2018.rds", sep = "")), area %in% c("27.3.a.20", "27.3.a.21", "27.3.c.22", "27.3.b.23", "27.3.d.24"))
```

#Catch
##Figures from catch vs. canums sheets

Minor differrences are expected, since some countries fill in the sheets with different number of digits - or it is read in differenly i R? I think it is the latter - read_excel don't always reads figures correct - don't know how to solve it.

Catch from the canum sheets are used in all the following calculations.

*The catch figurs are accepted*

```{r catch, echo=F, warning=F, results='asis'}
#Total
kable(merge(summarise(canum, catch_canum=sum(catch_t)/9), summarise(catch, catch_catch=sum(catch))))

#quarter country area
quarter<-merge(summarise(group_by(canum, ctry, quarter, area), catch_canum=sum(catch_t)/9), summarise(group_by(catch, ctry, quarter, area), catch_catch=sum(catch)))
quarter$diff<-quarter$catch_canum-quarter$catch_catch
kable(quarter)
```

## Catch per fleet

Figures from CANUM sheets

*Note Swedish catches from fleet D are combined with C - as always*

```{r, echo = F}
lan_fleet_plot <- summarise(group_by(canum, ctry, fleet, area), catch_ton = sum(catch_t, na.rm = T)/9)

ggplot(lan_fleet_plot, aes(x = paste(area, fleet, sep = " - "), y = catch_ton, fill = ctry)) +
  geom_bar(stat = "identity") +
    theme(legend.position="bottom")


kable(lan_fleet <- summarise(group_by(canum, ctry, fleet, area, quarter), catch_canum = sum(catch_t)/9))

```

## Mean weight per age

```{r, echo = F}

ggplot(filter(canum, weca_g != 0), aes(x = wr, y = weca_g, group = ctry, col = ctry)) +
  geom_point() +
  geom_line() +
  facet_grid(quarter~area+fleet) +
    theme(legend.position="bottom")

```

## Mean length per age

```{r, echo = F}

ggplot(filter(canum, leca_cm != 0), aes(x = wr, y = leca_cm, group = ctry, col = ctry)) +
  geom_point() +
  geom_line() +
  facet_grid(quarter~area+fleet) +
    theme(legend.position="bottom")

```

