---
title: "C4 - Imputations - overview missing"
author: "Kirsten Birch H?kansson, DTU Aqua"
date: \today
output: pdf_document
---

#Documentation
This program reads in the canum, make an overview of landings with and without samples

What to do;

1.  run this program
2.  manually fill landings without samples in the file outputted - rename the file to _filled
3.  run C5_imputations


General method for filling in (Lotte's method): 
In general samples from the same country are used. Only borrow  between 1st and 2nd quarter, and 3rd and 4th....


2017 - special concerns - not borrowing Norwegian samples, since there figure are model with a model that include - only one sample in 

```{r setup, include=F}
library(dplyr)
library(sqldf)

options("scipen" = 1000)
dataPath <- "Q:/mynd/Assessement_discard_and_the_like/WG/HAWG/WBSS_SC/wg_HAWG/WBSS/compile_input_data/catch/data/2019/results/"
```

##Read in data and trim number of variables
```{r input, include=F}
canum <- readRDS(paste(dataPath,"C1_her2024_canum_without_imputations_2018.rds", sep=""))

names(canum)

canum1<-canum[, c("ctry","year","area","fleet","quarter","sppName","wr","canum_1000","weca_g","leca_cm","catch_t","noSample","noLength","noAge")]

#Check if figures are unique

test<-distinct(canum1, ctry, year, area, fleet, quarter, sppName, wr, noSample, noLength, noAge)

length(unique(canum1$ctry))
6*1*7*4*9

6*1*7*4

#The canum looks fine

```

##Overview of sampling and strat with missing 
Output table where the imputation should be recorded
```{r output, include=F}

canum1$canum_1000 <-
  ifelse(is.na(canum1$canum_1000), 0, canum1$canum_1000)
canumSum <-
  aggregate(
    canum_1000 ~ ctry + year + area + fleet + quarter + sppName + catch_t +
      noSample + noLength + noAge,
    data = canum1,
    FUN = sum
  )
canumSum <- rename(canumSum, canumTotal = canum_1000)

canumSum$comment <-
  ifelse(
    canumSum$canumTotal > 0 &
      canumSum$noSample == 0,
    "National imputation",
    ifelse(
      canumSum$catch_t == 0,
      "No landings",
      ifelse(canumSum$noSample > 0, "Sampling", "")
    )
  )

canumSum$useCtry <-
  ifelse(canumSum$noSample > 0 |
           canumSum$comment == "National imputation",
         canumSum$ctry,
         "")
canumSum$useArea <-
  ifelse(canumSum$noSample > 0 |
           canumSum$comment == "National imputation",
         canumSum$area,
         "")
canumSum$useFleet <-
  ifelse(canumSum$noSample > 0 |
           canumSum$comment == "National imputation",
         canumSum$fleet,
         "")
canumSum$useQuarter <-
  ifelse(canumSum$noSample > 0 |
           canumSum$comment == "National imputation",
         canumSum$quarter,
         "")

write.table(
  canumSum,
  paste(dataPath, "C4_her2024_missing_bio_2018.csv", sep = ""),
  sep = ",",
  row.names = F
)
```
