---
date: "15. Marts 2019"
output:
  word_document:
    reference_docx: input_tables_SAM_word_style.docx
---

```{r info, include=F}

#This script reads in data and tables directly from www.stockassessment.org

#Remember to save the reference docx for styles the same place at the rmd script - input_tables_SAM_word_style.docx

#To insure that each table starts on a new pages Page Break are inserted - these need to be deleted from the final document

```


```{r setup, include=FALSE}
library(pander)
library(stockassessment)
library(htmltab)
library(dplyr)
library(reshape2)

options(scipen = 999)

#Multi fleet 
dir_dat<-"https://www.stockassessment.org/datadisk/stockassessment/userdirs/user278/WBSS_HAWG_2019_draft/data/" #input data directly from www.stockassessment.org


#single fleet
dir_dat_single<-"https://www.stockassessment.org/datadisk/stockassessment/userdirs/user278/WBSS_HAWG_2019_sf_draft/data/" #input data directly from www.stockassessment.org

panderOptions("table.style", "rmarkdown")
panderOptions("table.alignment.default", "right")
panderOptions('table.split.table', Inf)

knitr::opts_chunk$set(echo=F, warning=F, message=F)

```


**TABLE 3.6.1.a    -    WESTERN BALTIC SPRING SPAWNING HERRING**\
*Single fleet*\
Catch in number (CANUM, thousands)

```{r, echo=F}
cn<-read.ices(paste(dir_dat_single,"cn.dat", sep=""))
pander(cn)
```

##### Page Break

**TABLE 3.6.1.b - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet A*\
Catch in number (CANUM, thousands)

```{r, echo=F}
cn_A<-read.ices(paste(dir_dat,"cn_A.dat", sep=""))
pander(cn_A)
```

##### Page Break

**TABLE 3.6.1.c - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet C*\
Catch in number (CANUM, thousands)

```{r, echo=F}
cn_C<-read.ices(paste(dir_dat,"cn_C.dat", sep=""))
pander(cn_C)
```

##### Page Break

**TABLE 3.6.1.d - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet D*\
Catch in number (CANUM, thousands)

```{r, echo=F}
cn_D<-read.ices(paste(dir_dat,"cn_D.dat", sep=""))
pander(cn_D)
```

##### Page Break

**TABLE 3.6.1.e - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet F*\
Catch in number (CANUM, thousands)

```{r, echo=F}
cn_F<-read.ices(paste(dir_dat,"cn_F.dat", sep=""))
pander(cn_F)
```

##### Page Break

**TABLE 3.6.2.a    -    WESTERN BALTIC SPRING SPAWNING HERRING**\
*Single fleet*\
Weight at age as W-ringers in the catch (WECA, kg)

```{r, echo=F}
cw<-round(read.ices(paste(dir_dat_single,"cw.dat", sep="")), digits=4)
cw<-format(cw, digits=4, nsmall=4)
pander(cw)
```

##### Page Break

**TABLE 3.6.2.b - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet A*\
Weight at age as W-ringers in the catch (WECA, kg)

```{r, echo=F}
cw_A<-round(read.ices(paste(dir_dat,"cw_A.dat", sep="")), digits=4)
cw_A<-format(cw_A, digits=4, nsmall=4)
pander(cw_A)
```

##### Page Break

**TABLE 3.6.2.c - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet C*\
Weight at age as W-ringers in the catch (WECA, kg)

```{r, echo=F}
cw_C<-round(read.ices(paste(dir_dat,"cw_C.dat", sep="")), digits=4)
cw_C<-format(cw_C, digits=4, nsmall=4)
pander(cw_C)
```

##### Page Break

**TABLE 3.6.2.d - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet D*\
Weight at age as W-ringers in the catch (WECA, kg)

```{r, echo=F}
cw_D<-round(read.ices(paste(dir_dat,"cw_D.dat", sep="")), digits=4)
cw_D<-format(cw_D, digits=4, nsmall=4)
pander(cw_D)
```

##### Page Break

**TABLE 3.6.2.e - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet - Fleet F*\
Weight at age as W-ringers in the catch (WECA, kg)

```{r, echo=F}
cw_F<-round(read.ices(paste(dir_dat,"cw_F.dat", sep="")), digits=4)
cw_F<-format(cw_F, digits=4, nsmall=4)
pander(cw_F)
```

##### Page Break

**TABLE 3.6.3 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Weight at age as W-ringers in the stock (WEST, kg)

```{r, echo=F}
sw<-round(read.ices(paste(dir_dat,"sw.dat", sep="")), digits=4)
sw<-format(sw, digits=4, nsmall=4)
pander(sw)
```

##### Page Break

**TABLE 3.6.4 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Natural mortality (NATMOR)

```{r, echo=F}
nm<-read.ices(paste(dir_dat,"nm.dat", sep=""))
pander(nm)
```

##### Page Break

**TABLE 3.6.5 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Proportion mature (MATPROP)

```{r, echo=F}
mo<-read.ices(paste(dir_dat,"mo.dat", sep=""))
pander(mo)
```

##### Page Break

**TABLE 3.6.6 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Fraction of harvest before spawning (FPROP)

```{r, echo=F}
pf<-read.ices(paste(dir_dat,"pf.dat", sep=""))
pander(pf)
```

##### Page Break

**TABLE 3.6.7 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Fraction of natural mortality before spawning (MPROP)

```{r, echo=F}
pm<-read.ices(paste(dir_dat,"pm.dat", sep=""))
pander(pm)
```

##### Page Break

**TABLE 3.6.8 - WESTERN BALTIC SPRING SPAWNING HERRING**\
*Multi fleet & single fleet*\
Survey indices: HERAS (number)

```{r, echo=F}
survey<-read.ices(paste(dir_dat,"survey.dat", sep=""))
pander(survey$HERAS)
```

##### Page Break

**TABLE 3.6.8 - WESTERN BALTIC SPRING SPAWNING HERRING, continued**\
*Multi fleet & single fleet*\
Survey indices: GerAS (number in thousands)

```{r, echo=F}
survey<-read.ices(paste(dir_dat,"survey.dat", sep=""))
pander(survey$GerAS)
```

##### Page Break

**TABLE 3.6.8 - WESTERN BALTIC SPRING SPAWNING HERRING, continued**\
*Multi fleet & single fleet*\
Survey indices: N20 (number in millions)

```{r, echo=F}
survey<-read.ices(paste(dir_dat,"survey.dat", sep=""))
pander(survey$N20)
```

##### Page Break

**TABLE 3.6.8 - WESTERN BALTIC SPRING SPAWNING HERRING, continued**\
*Multi fleet & single fleet*\
Survey indices: IBTS+BITS-Q1 (number per hour)

```{r, echo=F}
survey<-read.ices(paste(dir_dat,"survey.dat", sep=""))
pander(survey$`IBTS+BITS-Q1`)
```

##### Page Break

**TABLE 3.6.8 - WESTERN BALTIC SPRING SPAWNING HERRING, continued**\
*Multi fleet & single fleet*\
Survey indices: IBTS+BITS-Q3.4 (number per hour)

```{r, echo=F}
survey<-read.ices(paste(dir_dat,"survey.dat", sep=""))
pander(survey$`IBTS+BITS-Q3.4`)
```

