---
title: "WKHERRING - Multi fleet - split input data"
author: "Kirsten Birch Håkansson"
date: \today
output: pdf_document
---

Split CANUM, WECA - maybe CATON, but is should be CANUM * WECA

Combined fleet A with fleet C - do we want to do that? No - keep them seperate (Henrik) - done

Input:

WBSSH & NSASH_Input_14.06.2017.xlsx - file from Tomas\
Input files from assessment 2017 - from Valerio


```{r setup, include=FALSE}
library(readxl)
library(sqldf)
library(dplyr)
library(ggplot2)
library(reshape2)
options(scripen=9999, digits=4)

knitr::opts_chunk$set(fig.width=8, fig.height=8)

dir_in<-"X:/Assessement_discard_and_the_like/WG/WKHERRING/2017/mulitFleet/input/"
dir_out<-"X:/Assessement_discard_and_the_like/WG/WKHERRING/2017/mulitFleet/output/"
```

#What do we have?
Overviews based on the spreadsheet
```{r, echo=F, warning=FALSE, message=F}

#Read in data from spreadsheet and tidy  
canum<-read_excel(paste(dir_in,"WBSSH & NSASH_Input_14.06.2017.xlsx", sep=""), sheet=1)  
canum<-canum[,c(1:13)]
colnames(canum)<-c("year","stock","area","fleet","0","1","2","3","4","5","6","7","8")
canum1<-subset(canum, stock=="WBSS" & area!="TOTAL")
canumt<-melt(canum1, id=c("year","stock","area","fleet"))
colnames(canumt)<-c("year","stock","area","fleet","wr","number_mil")
canumt[is.na(canumt)] <- 0

weca<-read_excel(paste(dir_in,"WBSSH & NSASH_Input_14.06.2017.xlsx", sep=""), sheet=2) 
weca<-weca[,c(1:13)]
colnames(weca)<-c("year","stock","area","fleet","0","1","2","3","4","5","6","7","8")
weca1<-subset(weca, stock=="WBSS" & area!="TOTAL")
wecat<-melt(weca1, id=c("year","stock","area","fleet"))
colnames(wecat)<-c("year","stock","area","fleet","wr","mw_g")
wecat[is.na(wecat)] <- 0

caton<-merge(canumt,wecat)
caton$t_1000<-caton$number*caton$mw

caton_test<-summarise(group_by(caton, year, stock,area, fleet), t_1000=sum(t_1000))

```

\newpage

```{r}

canump<-summarise(group_by(canumt, year, stock, area), number_mil=sum(number_mil))
canump[canump==0] <- NA
ggplot(canump, aes(area, year )) +
  geom_tile(aes(fill = number_mil), color="white") +
  scale_fill_gradient(na.value="white", low="grey", high="black") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))

canump1<-summarise(group_by(canumt, year, stock, fleet), number_mil=sum(number_mil))
canump1[canump1==0] <- NA
ggplot(canump1, aes(fleet, year )) +
  geom_tile(aes(fill = number_mil), color="white") +
  scale_fill_gradient(na.value="white", low="grey", high="black") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))

canump2<-summarise(group_by(canumt, area, stock, fleet), number_mil=sum(number_mil))
canump2[canump2==0] <- NA
ggplot(canump2, aes(area, fleet)) +
  geom_tile(aes(fill = number_mil), color="white") +
  scale_fill_gradient(na.value="white", low="grey", high="black") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))

ggplot(subset(canump1, fleet %in% c("A","C","D","F") & year>1999), aes(year, number_mil, fill=fleet)) +
  geom_bar(stat = "identity")
```

#CANUM & WECA
```{r, message=F}
#read in original file

cn_txt = readLines(paste(dir_in, "cn.dat", sep=""),-1)
cn_txt1<-gsub(pattern = "\t", replace = "   ", x = cn_txt)

cw_txt = readLines(paste(dir_in, "cw.dat", sep=""),-1)
cw_txt1<-gsub(pattern = "\t", replace = "   ", x = cw_txt)

#Create new files
#canum & weca 1991-1999
cn_all<-cn_txt1
cn_all[1]=c("Herring in Sub-division 22-24 and Division IIIa (CANUM: Number in thousands), one fleet. 
            Figures same as in input file 2017")
cn_all[3]=c("1991 1999")
cn_all<-cn_all[1:14]
write.table(cn_all, paste(dir_out, "cn_all.dat", sep=""), row.names=F, col.names=F, quote=FALSE)

cw_all<-cw_txt1
cw_all[1]=c("Herring in SD 22-24 and Division IIIa (spring-spawners)(WECA: Mean weight in kg), one fleet. 
            Figures same as in input file 2017")
cw_all[3]=c("1991 1999")
cw_all<-cw_all[1:14]
write.table(cw_all, paste(dir_out, "cw_all.dat", sep=""), row.names=F, col.names=F, quote=FALSE)

#Per fleet 2000-2016
caton1<-subset(caton, !(area %in% c("22","23","24")) & !(fleet %in% c("C, D")) & year>1999)
distinct(caton1, area, fleet)

fak<-as.factor(caton1$fleet)

for(f in levels(fak)){catonf<-caton1[fak==f,]
cnf<-cn_txt1
cnf[1]=c(paste("Herring in Sub-division 22-24 and Division IIIa (CANUM: Number in thousands), fleet ", f, sep=""))
cnf[3]=c("2000 2016")
cnf<-cnf[1:5]

catonf[is.na(catonf)]<-0
catonf1<-summarise(group_by(catonf, year, stock, fleet, wr), number_mil=sum(number_mil))
catonft<-dcast(catonf1, year+stock+fleet~wr, sum)
catonft<-as.matrix(catonft[c(1:17),c(4:12)])*1000
catonft<-round(catonft, 0)
catonft1<-apply(catonft,1,paste, collapse="  ")
write.table(cnf, paste(dir_out, "cn_",f,".dat", sep=""), row.names=F, col.names=F, quote=FALSE)
write.table(catonft1, paste(dir_out, "cn_",f,".dat", sep=""), row.names=F, col.names=F, quote=FALSE, append=T)

cwf<-cw_txt1
cwf[1]=c(paste("Herring in SD 22-24 and Division IIIa (spring-spawners)(WECA: Mean weight in kg), fleet ", f, sep=""))
cwf[3]=c("2000 2016")
cwf<-cwf[1:5]

mwf<-summarise(group_by(catonf, year, stock, fleet, wr), mw_g=sum(t_1000)/sum(number_mil))
mw_ft<-dcast(mwf, year+stock+fleet~wr, sum)
mw_ft[is.na(mw_ft)]<-0
mw_ft<-as.matrix(mw_ft[c(1:17),c(4:12)])/1000
mw_ft<-round(mw_ft, 5)
mw_ft1<-apply(mw_ft,1,paste, collapse="  ")
write.table(cwf, paste(dir_out, "cw_",f,".dat", sep=""), row.names=F, col.names=F, quote=FALSE)
write.table(mw_ft1, paste(dir_out, "cw_",f,".dat", sep=""), row.names=F, col.names=F, quote=FALSE, append=T)

}

```

#Check data
##Compare with original input files
###CANUM (CN)
```{r}
cnorg<-read.table(paste(dir_in, "cn.dat", sep=""), skip=5)[c(10:26),]
colnames(cnorg)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")
cna<-read.table(paste(dir_out, "cn_A.dat", sep=""), skip=5)
cnc<-read.table(paste(dir_out, "cn_C.dat", sep=""), skip=5)
cnd<-read.table(paste(dir_out, "cn_D.dat", sep=""), skip=5)
cnf<-read.table(paste(dir_out, "cn_F.dat", sep=""), skip=5)

cnnew<-cna+cnc+cnd+cnf
colnames(cnnew)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")
cnnew1<-cnnew
cnnew1$year<-c(2000:2016)

#Sum of canum from input files with fleet - these figures should equal the figures in the spreadsheet
cnnew1

cncom<-cnorg-cnnew
cncom$year<-c(2000:2016)
#Difference in canum between the original input file and sum of input files per fleet
cncom

cncom_pct<-round(((cnorg-cnnew)/cnorg)*100, 2)
cncom_pct$year<-c(2000:2016)
#Pct. difference in canum between the original input file and sum of input files per fleet
cncom_pct

```


###CATON
CATON has not been made by fleet, so testing CANUM*WECA against the CATON used in the model presently

```{r}
ctorg<-read.table(paste(dir_in, "CATON.dat", sep=""), skip=5)[c(10:26),]
cwa<-read.table(paste(dir_out, "cw_A.dat", sep=""), skip=5)
cwc<-read.table(paste(dir_out, "cw_C.dat", sep=""), skip=5)
cwd<-read.table(paste(dir_out, "cw_D.dat", sep=""), skip=5)
cwf<-read.table(paste(dir_out, "cw_F.dat", sep=""), skip=5)

cta<-cna*cwa
ctc<-cnc*cwc
ctd<-cnd*cwd
ctf<-cnf*cwf

ctnew<-cta+ctc+ctd+ctf
colnames(ctnew)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")
ctnew1<-ctnew
ctnew1$year<-c(2000:2016)
ctnew1$totalNew<-ctnew1$wr0+ctnew1$wr1+ctnew1$wr2+ctnew1$wr3+ctnew1$wr4+ctnew1$wr5+ctnew1$wr6+ctnew1$wr7+ctnew1$wr8
ctnew1$totalOrg<-ctorg
ctnew1$diffTon<-ctnew1$totalOrg-ctnew1$totalNew
ctnew1$diffPct<-(ctnew1$diffTon/ctnew1$totalOrg)*100

#Difference in CATON betweeen new and original input file
ctnew1[,c(10:14)]
```

###WECA
```{r}
cworg<-read.table(paste(dir_in, "cw.dat", sep=""), skip=5)[c(10:26),]
colnames(cworg)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")
cwnew<-(ctnew/cnnew)
colnames(cwnew)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")

cwcom<-round(cworg-cwnew, digits=5)
cwcom$year<-c(2000:2016)
#Difference in WECA between the original input file and sum of input files per fleet
cwcom
```

###CATON
Files presently used in the model: Testing CANUMxWECA againt CATON
```{r}
cncworg<-cnorg*cworg
colnames(cncworg)<-c("wr0","wr1","wr2","wr3","wr4","wr5","wr6","wr7","wr8")
cncworg$year<-c(2000:2016)
cncworg$caton_cnxcw<-cncworg$wr0+cncworg$wr1+cncworg$wr2+cncworg$wr3+cncworg$wr4+cncworg$wr5+cncworg$wr6+cncworg$wr7+cncworg$wr8
cncworg$caton_CATON<-ctorg
cncworg$diffTon<-cncworg$caton_cnxcw-cncworg$caton_CATON
cncworg$diffPct<-(cncworg$diffTon/cncworg$caton_cnxcw)*100

#Difference in CATON betweeen the CATON file and cs*cn used presently
cncworg[,c(10:14)]
```

