---
output: 
  word_document:
    reference_docx: ../_Common/report_template_v1.5.dotx
---

```{r setup, include=FALSE}
# ==============================================================================
# Irish Sea herring; quality control (and miscellaneous visualization)
#
# 25/03/2020 Adapted from North Sea herring; Martin Pastoors
# ==============================================================================

require("knitr")
knitr::opts_chunk$set(
  echo = FALSE,	message = FALSE,	warning = FALSE,	comment = "",	crop = TRUE, fig.width=10) 

rm(list=ls())

#library(devtools)  ## install.packages("devtools")
library(FLCore)
library(FLSAM)
library(tidyverse)
library(RColorBrewer)

# local path (not needed in RMarkdown)

# source publication theme
source("../_common/theme_publication.r")

# Load crayola code
source("../_common/crayola.r")

# Create QC directory
dir.create("qc",showWarnings = FALSE)

# Other settings
output.dir          <-  file.path(".","qc/")              # result directory\



# read in data objects of year1
y1               <- 2019
dir1             <- "//community.ices.dk@SSL/DavWWWRoot/ExpertGroups/HAWG/2019 Meeting Docs/06. Data/IrishSea"
assessment_name1 <- 'ISH_assessment 2019'

load(file.path(dir1, paste0(assessment_name1, ".RData"))) 
s.y1             <- ISH
s.ctrl.y1        <- ISH.ctrl
s.sam.y1         <- ISH.sam
s.tun.y1         <- ISH.tun
ly.y1            <- an(range(s.y1)["maxyear"])
# stf.y1    <- get(load(file.path('stf',y1,paste0('NSAS_stf_',y1,'_FmsyAR.RData'))))[["stf"]]

# read in data objects of year1
y2               <- 2020
dir2             <- 
  "//community.ices.dk@SSL/DavWWWRoot/ExpertGroups/HAWG/2020 Meeting Docs/06. Data/her.27.nirs/SAM/results"
assessment_name2 <- 'ISH_assessment 2020'

load(file.path(dir2, paste0(assessment_name2, ".RData"))) 
s.y2      <- ISH
s.ctrl.y2 <- ISH.ctrl
s.sam.y2  <- ISH.sam
s.tun.y2  <- ISH.tun
ly.y2     <- an(range(s.y2)["maxyear"])
# stf.y2    <- get(load("D:/GIT/wg_HAWG/NSAS/stf/NSAS_stf_CD_TAC_sq_2020_FmsyAR.Rdata"))[["stf"]]


rm(ISH, ISH.ctrl, ISH.sam, ISH.tun)

```

**Quality control of `r assessment_name2` assessment**

**Martin Pastoors^1^**

`r format(Sys.time(), '%d/%m/%Y %H:%M')`


```{r echo=FALSE, fig.align="center", fig.asp=1.2, message=FALSE, warning=FALSE}

# Figure 2.2.4.x1 Data check on biological input data 
df.y1 <- as.data.frame(s.y1) %>% mutate(assessmentyear = ac(y1)) 
df.y2 <- as.data.frame(s.y2) %>% mutate(assessmentyear = ac(y2)) 
  
bind_rows(df.y1, df.y2) %>%
  filter(slot %in% c("catch", "catch.n","catch.wt", "harvest.spwn", "m.spwn","m","mat", "stock.wt")) %>% 
  ggplot(aes(x=year, y=data)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_line(aes(colour=assessmentyear)) +
  # labs(title=myvar) +
  facet_grid(slot~age, scale="free_y")

```

**Figure 2.2.4.x1. Irish Sea Herring. Data check on biological input data, comparing data of the `r y1` and `r y2` assessments.**

```{r echo=FALSE, fig.align="center", fig.asp=1.0, message=FALSE, warning=FALSE}

# Figure 2.2.4.x2 Data check on biological input data 
# df.y1 <- as.data.frame(s.y1) %>% mutate(assessmentyear = ac(y1)) 
# df.y2 <- as.data.frame(s.y2) %>% mutate(assessmentyear = ac(y2)) 
  
bind_rows(df.y1, df.y2) %>%
  filter(slot %in% c("catch", "catch.n","catch.wt", "harvest.spwn", "m.spwn","m","mat", "stock.wt")) %>% 
  filter(data != -1) %>% 
  arrange(slot, age, year, unit, season, area, iter, assessmentyear) %>% 
  group_by(slot, age, year, unit, season, area, iter) %>% 
  mutate(data1 = lag(data, n=1)) %>% 
  filter(data1 != -1, !is.na(data1)) %>% 
  mutate(perc = 100*((data1-data)/data)) %>% 
  # filter(perc > 0) %>% 
  # View()

  ggplot(aes(x=year, y=perc)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_hline(yintercept=0, colour="black", linetype="dashed") +
  geom_line(colour="red", size=1) +
  labs(y="perc diff") +
  facet_grid(slot~age)

```

**Figure 2.2.4.x2. Irish Sea Herring. Data check on biological input data, relative difference between the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.7, message=FALSE, warning=FALSE}

# Figure 2.2.4.x3 Data check on survey input data 
df.tun.y1 <- as.data.frame(s.tun.y1) %>% mutate(assessmentyear = ac(y1)) 
df.tun.y2 <- as.data.frame(s.tun.y2) %>% mutate(assessmentyear = ac(y2)) 

bind_rows(df.tun.y1, df.tun.y2) %>%
  filter(slot %in% c("index")) %>% 
  ggplot(aes(x=year, y=data)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_line(aes(colour=assessmentyear)) +
  # labs(title=myvar) +
  facet_grid(cname~age, scale="free_y")

```

**Figure 2.2.4.x4. Irish Sea Herring. Data check on survey input data, relative difference between the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.7, message=FALSE, warning=FALSE}

# Figure 2.2.4.x4 Data check on relative difference in survey input data 
df.tun.y1 <- as.data.frame(s.tun.y1) %>% mutate(assessmentyear = ac(y1)) 
df.tun.y2 <- as.data.frame(s.tun.y2) %>% mutate(assessmentyear = ac(y2)) 

bind_rows(df.tun.y1, df.tun.y2) %>%
      filter(slot=="index") %>%
      filter(data != -1) %>% 
      arrange(slot, age, year, unit, season, area, iter, cname, assessmentyear) %>% 
      group_by(slot, age, year, unit, season, area, iter, cname) %>% 
      mutate(data1 = lag(data, n=1)) %>% 
      filter(data1 != -1) %>% 
      mutate(perc = 100*((data1/data)-1)) %>% 
      
      ggplot(aes(x=year, y=perc)) +
      theme_bw() +
      theme(legend.position="none") +
      geom_hline(yintercept=0, colour="black", linetype="dashed") +
      geom_line(colour="red", size=1) +
      labs(x="",y="") +
      facet_grid(cname~age)


```

**Figure 2.2.4.x4. Irish Sea Herring. Data check on survey input data, comparing data of the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.6.1.2, Crayola catch

# trim(slot(s.y2,"catch.n"), year=(ly.y2-25):ly.y2, age=0:8) %>% 
s.y2@catch.n %>% 
  as.data.frame() %>% 
  dplyr::select(year, age, number = data) %>% 
  filter(number != -1) %>% 
  crayola(., t="Irish Sea herring catch at age")

```

**Figure 2.6.1.2. Irish Sea Herring. Time series of catch-at-age proportion at age as used in the Irish Sea herring assessment. Colours indicate year-classes. All ages are scaled independently and therefore the size of the bars can only be compared within an age.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.6.1.4, Crayola acoustic survey

# trim(s.tun.y2[["HERAS"]]@index, year=(ly.y2-25):ly.y2, age=1:8) %>% 
s.tun.y2[[1]] %>% 
  as.data.frame() %>% 
  dplyr::select(year, age, number = data) %>% 
  filter(number != -1) %>% 
  crayola(., t = "Irish Sea acoustic survey")


```

**Figure 2.6.1.4. Irish Sea Herring. Time series of the Irish Sea acoustic index by age. Colours indicate year-classes. All ages are scaled independently and cannot be compared between ages.**

