---
output: 
  word_document:
    reference_docx: ../_Common/report_template_v1.5.dotx
---

```{r setup, include=FALSE}
# ==============================================================================
# North Sea herring; quality control (and miscellaneous visualization)
#
# 22/03/2020 first coding
# ==============================================================================

require("knitr")
knitr::opts_chunk$set(
  echo = FALSE,	message = FALSE,	warning = FALSE,	comment = "",	crop = TRUE, fig.width=10) 
rm(list=ls())

#library(devtools)  ## install.packages("devtools")
library(FLCore)
library(FLSAM)
library(tidyverse)
library(RColorBrewer)

# local path (not needed in RMarkdown)

# source publication theme
source("../_common/theme_publication.r")

# Load crayola code
source("../_common/crayola.r")

# Create QC directory
dir.create("qc",showWarnings = FALSE)

# Other settings
output.dir          <-  file.path(".","qc/")              # result directory\

assessment_name     <- 'NSH_HAWG2020_sf'
y1                  <- 2019
y2                  <- 2020

# read in data objects of previous year
load("//community.ices.dk@SSL/DavWWWRoot/ExpertGroups/HAWG/2019 Meeting Docs/06. Data/NSAS/NSH_HAWG2019_sf.Rdata") 
s.y1      <- NSH
s.ctrl.y1 <- NSH.ctrl
s.sam.y1  <- NSH.sam
s.tun.y1  <- NSH.tun
ly.y1     <- an(range(s.y1)["maxyear"])

stf.y1    <- get(load(file.path('stf',y1,paste0('NSAS_stf_',y1,'.RData'))))#[["stf"]]


load("//community.ices.dk@SSL/DavWWWRoot/ExpertGroups/HAWG/2020 Meeting Docs/06. Data/her.27.3a47d/NSH_HAWG2020_sf.Rdata")
s.y2      <- NSH
s.ctrl.y2 <- NSH.ctrl
s.sam.y2  <- NSH.sam
s.tun.y2  <- NSH.tun
ly.y2     <- an(range(s.y2)["maxyear"])

stf.y2    <- get(load(file.path('stf',paste0('NSAS_stf_',y2,'.RData'))))#[["stf"]]

rm(NSH, NSH.ctrl, NSH.sam, NSH.tun)

```

**Quality control of `r assessment_name` assessment**

**Martin Pastoors^1^**

`r format(Sys.time(), '%d/%m/%Y %H:%M')`


```{r echo=FALSE, fig.align="center", fig.asp=1.0, message=FALSE, warning=FALSE}

# Figure 2.2.4.x1 Data check on biological input data 
df.y1 <- as.data.frame(s.y1) %>% mutate(assessmentyear = ac(y1)) 
df.y2 <- as.data.frame(s.y2) %>% mutate(assessmentyear = ac(y2)) 
  
bind_rows(df.y1, df.y2) %>%
  filter(slot %in% c("catch", "catch.n","catch.wt", "harvest.spwn", "m.spwn","m","mat", "stock.wt")) %>% 
  ggplot(aes(x=year, y=data)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_line(aes(colour=assessmentyear)) +
  # labs(title=myvar) +
  facet_grid(slot~age, scale="free_y")

```

**Figure 2.2.4.x1. North Sea Herring. Data check on biological input data, comparing data of the `r y1` and `r y2` assessments.**

```{r echo=FALSE, fig.align="center", fig.asp=1.0, message=FALSE, warning=FALSE}

# Figure 2.2.4.x2 Data check on biological input data 
# df.y1 <- as.data.frame(s.y1) %>% mutate(assessmentyear = ac(y1)) 
# df.y2 <- as.data.frame(s.y2) %>% mutate(assessmentyear = ac(y2)) 
  
bind_rows(df.y1, df.y2) %>%
  filter(slot %in% c("catch", "catch.n","catch.wt", "harvest.spwn", "m.spwn","m","mat", "stock.wt")) %>% 
  filter(data != -1) %>% 
  arrange(slot, age, year, unit, season, area, iter, assessmentyear) %>% 
  group_by(slot, age, year, unit, season, area, iter) %>% 
  mutate(data1 = lag(data, n=1)) %>% 
  filter(data1 != -1, !is.na(data1)) %>% 
  mutate(perc = 100*((data1/data)-1)) %>% 

  ggplot(aes(x=year, y=perc)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_hline(yintercept=0, colour="black", linetype="dashed") +
  geom_line(colour="red", size=1) +
  labs(y="perc diff") +
  facet_grid(slot~age)

```

**Figure 2.2.4.x2. North Sea Herring. Data check on biological input data, relative difference between the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=1.0, message=FALSE, warning=FALSE}

# Figure 2.2.4.x3 Data check on survey input data 
df.tun.y1 <- as.data.frame(s.tun.y1) %>% mutate(assessmentyear = ac(y1)) 
df.tun.y2 <- as.data.frame(s.tun.y2) %>% mutate(assessmentyear = ac(y2)) 

bind_rows(df.tun.y1, df.tun.y2) %>%
  filter(slot %in% c("index")) %>% 
  ggplot(aes(x=year, y=data)) +
  theme_publication() +
  theme(legend.position="bottom") +
  geom_line(aes(colour=assessmentyear)) +
  # labs(title=myvar) +
  facet_grid(cname~age, scale="free_y")

```

**Figure 2.2.4.x4. North Sea Herring. Data check on survey input data, relative difference between the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=1.0, message=FALSE, warning=FALSE}

# Figure 2.2.4.x4 Data check on relative difference in survey input data 
df.tun.y1 <- as.data.frame(s.tun.y1) %>% mutate(assessmentyear = ac(y1)) 
df.tun.y2 <- as.data.frame(s.tun.y2) %>% mutate(assessmentyear = ac(y2)) 

bind_rows(df.tun.y1, df.tun.y2) %>%
      filter(slot=="index") %>%
      filter(data != -1) %>% 
      arrange(slot, age, year, unit, season, area, iter, cname, assessmentyear) %>% 
      group_by(slot, age, year, unit, season, area, iter, cname) %>% 
      mutate(data1 = lag(data, n=1)) %>% 
      filter(data1 != -1) %>% 
      mutate(perc = 100*((data1/data)-1)) %>% 
      
      ggplot(aes(x=year, y=perc)) +
      theme_bw() +
      theme(legend.position="none") +
      geom_hline(yintercept=0, colour="black", linetype="dashed") +
      geom_line(colour="red", size=1) +
      labs(x="",y="") +
      facet_grid(cname~age)


```

**Figure 2.2.4.x4. North Sea Herring. Data check on survey input data, comparing data of the `r y1` and `r y2` assessments.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.6.1.2, Crayola catch

trim(slot(s.y2,"catch.n"), year=(ly.y2-25):ly.y2, age=0:8) %>% 
  as.data.frame() %>% 
  dplyr::select(year, age, number = data) %>% 
  filter(number != -1) %>% 
  crayola(., t="North Sea herring catch at age")

```

**Figure 2.6.1.2. North Sea Herring. Time series of catch-at-age proportion at ages 0–8+ as used in the North Sea herring assessment. Colours indicate year-classes. All ages are scaled independently and therefore the size of the bars can only be compared within an age.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.6.1.4, Crayola heras

trim(s.tun.y2[["HERAS"]]@index, year=(ly.y2-25):ly.y2, age=1:8) %>% 
  as.data.frame() %>% 
  dplyr::select(year, age, number = data) %>% 
  filter(number != -1) %>% 
  crayola(., t = "North Sea herring HERAS survey")


```

**Figure 2.6.1.4. North Sea Herring. Time series of the HERAS acoustic index by age 1–8+. Colours indicate year-classes. All ages are scaled independently and cannot be compared between ages.**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.7.2.1. Predicted and projected catch (in weight) 

catch.y1  <- as.data.frame(stf.y1@catch.n * stf.y1@catch.wt) %>% mutate(stf=ac(y1))
catch.y2  <- as.data.frame(stf.y2@catch.n * stf.y2@catch.wt) %>% mutate(stf=ac(y2))

bind_rows(catch.y1,catch.y2) %>% 
  mutate(age = paste0(age," wr")) %>% 
  filter(unit=="A") %>% 

  ggplot(aes(x=year, y=data, group=stf)) +
  theme_publication() +
  geom_line(aes(colour=stf), size=1) +
  labs(x="", y="catch (tonnes)", colour="HAWG") +
  facet_wrap(~age)

```

**Figure 2.7.2.1. North Sea Herring. Predicted and projected catch (in weight) between `r y1` assessment (`r y1+1` as forecast year) and `r y2` assessment (`r y2+1` as forecast year).**

##### page break

```{r echo=FALSE, fig.align="center", fig.asp=0.6, message=FALSE, warning=FALSE}

# Figure 2.7.2.2. Predicted and projected catch (in weight) 

catch.y1  <- as.data.frame(stf.y1@catch.n * stf.y1@catch.wt) %>% mutate(stf=ac(y1))
catch.y2  <- as.data.frame(stf.y2@catch.n * stf.y2@catch.wt) %>% mutate(stf=ac(y2))

bind_rows(catch.y1,catch.y2) %>% 
  mutate(age = paste0(age," wr")) %>% 
  mutate(stf = paste0("HAWG ", stf)) %>% 
  filter(unit=="A") %>% 

  ggplot(aes(x=year, y=data, group=stf)) +
  theme_bw() +
  geom_bar(aes(fill=as.character(age)), stat="identity", colour="white") +
  labs(x = "", y= "catch (tonnes)", fill="age (WR)") +
  facet_wrap(~stf)

```

**Figure 2.7.2.2. North Sea Herring. Catch proportions for the different ages between the  `r y1` assessment (`r y1+1` as forecast year) and `r y2` assessment (`r y2+1` as forecast year).**

